Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-10-28 Tex/Old text/chapters/appendixB.tex
Thesis update

\begin{itemize}
\item \textbf{Block 1}: global variables declaration, with weather data from location (minimum and maximum solar irradiance and temperature, for 24-hour of the day) as array, requirements, and data sheet information from each equipment of the PV system that will be verified.

\item \textbf{Block 2}: support functions (logarithm of natural order, exponential)

\item \textbf{Block 3}: PV system specific functions (charge battery, discharge battery, PV panel generation, sizing check)

@@

\begin{itemize}
\item \textbf{Block 1}: global variables declaration, with weather data from location, requirements, and data sheet information from each equipment of the PV system that will be verified.

\item \textbf{Block 2}: support functions (start value with lowest cost for the list of equipment, synthesis phase function to obtain feasible technical solutions with model checking)

\item \textbf{Block 3}: main code with the iterative control of the verify phase
\end{itemize}

@@

\begin{itemize}
\item Minimum and maximum solar irradiance (average value for the 24-hour of the day) from location
\item Minimum and maximum temperature (average for every month of the year)
\item Local insolation (average number of sun hours by day at the location)
\item Number of solar panels in series
\item Number of solar panels in parallel
\item Number of series-connected cells from each solar panel
\item Nominal Operating Cell Temperature
\item Reference solar irradiance
\item Reference temperature
\item Short-circuit current temperature coefficient
\item Open-circuit voltage temperature coefficient
\item Reference short-circuit current
\item Reference open-circuit voltage
\item Reference maximum current, voltage, and power
\item Minimum MPPT voltage
\item Operation current
\item Solar panel efficiency
\item Panel area in square meters
\item DC-bus voltage
\item Individual battery voltage
\item Battery bank capacity
\item State of charge limit
\item Number of batteries in series
\item Number of batteries in parallel
\item Autonomy of the batteries
\item Efficiency from batteries
\item Float, absorption and bulk battery voltages
\item Charge controller efficiency
\item Charge controller current
\item Charge controller maximum voltage
\item Inverter output voltage
\item Inverter AC reference power
\item Inverter maximum (surge) AC power reference
\item AC voltage (outlet standard)
\item Power demand from the house
\item Surge demand from the house
\item Energy consumption from the house
\end{itemize}

@@

\begin{itemize}
\item Minimum and maximum solar irradiance (average value for the 24-hour of the day) from location
\item Minimum and maximum temperature (average for every month of the year)
\item Local insolation (average number of sun hours by day at the location)
\item DC-bus voltage
\item Autonomy of the batteries
\item State of charge limit
\item Individual battery voltage
\item Reference solar irradiance
\item Reference temperature
\item For every item of solar PV panel list, as a matrix (area, efficiency, number of series-connected cells, Nominal Operating Cell Temperature, short-circuit current temperature coefficient, open-circuit voltage temperature coefficient, reference short-circuit current, reference open-circuit voltage, reference maximum power, reference maximum current, reference maximum voltage, maximum voltage on NOCT, cost in US dollars)
\item For every item of batteries list, as a matrix (efficiency, voltage, capacity $C_{20}$), bulk voltage, float voltage, cost in US dollars)
\item For every item of charge controller list, as a matrix (efficiency, nominal current, voltage  output, minimum MPPT voltage, maximum current, cost in US dollars)
\item For every item of inverter list, as a matrix (efficiency, input DC voltage, output AC voltage, reference AC power, reference maximum AC power, cost in US dollars)
\item AC voltage (outlet standard)
\item Power demand from the house
\item Surge demand from the house
\item Energy consumption from the house
\end{itemize}

@@

ESBMC can be downloaded from its GitHub in \url{https://github.com/esbmc/esbmc}. Installation commands can be found in \url{https://ssvlab.github.io/esbmc/documentation.html}.

Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3.

@@

The command-line in Linux is: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c.

>>>>

\begin{itemize}
\item \textbf{Block 1}: global variables declaration, with weather data from location (minimum and maximum solar irradiance and temperature, for 24-hour of the day) as array, requirements, and data sheet information from each equipment of the PV system that will be verified;

\item \textbf{Block 2}: support functions (logarithm of natural order, exponential);

\item \textbf{Block 3}: PV system specific functions (charge battery, discharge battery, PV panel generation, sizing check);

@@

\begin{itemize}
\item \textbf{Block 1}: global variables declaration, with weather data from location, requirements, and data sheet information from each equipment of the PV system that will be verified;

\item \textbf{Block 2}: support functions (start value with lowest cost for the list of equipment, synthesis phase function to obtain feasible technical solutions with model checking);

\item \textbf{Block 3}: main code with the iterative control of the verify phase.
\end{itemize}

@@

\begin{itemize}
\item Minimum and maximum solar irradiance (average value for the 24-hour of the day) from location;
\item Minimum and maximum temperature (average for every month of the year);
\item Local insolation (average number of sun hours by day at the location);
\item Number of solar panels in series;
\item Number of solar panels in parallel;
\item Number of series-connected cells from each solar panel;
\item Nominal Operating Cell Temperature;
\item Reference solar irradiance;
\item Reference temperature;
\item Short-circuit current temperature coefficient;
\item Open-circuit voltage temperature coefficient;
\item Reference short-circuit current;
\item Reference open-circuit voltage;
\item Reference maximum current, voltage, and power;
\item Minimum MPPT voltage;
\item Operation current;
\item Solar panel efficiency;
\item Panel area in square meters;
\item DC-bus voltage;
\item Individual battery voltage;
\item Battery bank capacity;
\item State of charge limit;
\item Number of batteries in series;
\item Number of batteries in parallel;
\item Autonomy of the batteries;
\item Efficiency from batteries;
\item Float, absorption and bulk battery voltages;
\item Charge controller efficiency;
\item Charge controller current;
\item Charge controller maximum voltage;
\item Inverter output voltage;
\item Inverter AC reference power;
\item Inverter maximum (surge) AC power reference;
\item AC voltage (outlet standard);
\item Power demand from the house;
\item Surge demand from the house;
\item Energy consumption from the house.
\end{itemize}

@@

\begin{itemize}
\item Minimum and maximum solar irradiance (average value for the 24-hour of the day) from location;
\item Minimum and maximum temperature (average for every month of the year);
\item Local insolation (average number of sun hours by day at the location);
\item DC-bus voltage;
\item Autonomy of the batteries;
\item State of charge limit;
\item Individual battery voltage;
\item Reference solar irradiance;
\item Reference temperature;
\item For every item of solar PV panel list, as a matrix (area, efficiency, number of series-connected cells, Nominal Operating Cell Temperature, short-circuit current temperature coefficient, open-circuit voltage temperature coefficient, reference short-circuit current, reference open-circuit voltage, reference maximum power, reference maximum current, reference maximum voltage, maximum voltage on NOCT, cost in US dollars);
\item For every item of batteries list, as a matrix (efficiency, voltage, capacity $C_{20}$), bulk voltage, float voltage, cost in US dollars);
\item For every item of charge controller list, as a matrix (efficiency, nominal current, voltage  output, minimum MPPT voltage, maximum current, cost in US dollars);
\item For every item of inverter list, as a matrix (efficiency, input DC voltage, output AC voltage, reference AC power, reference maximum AC power, cost in US dollars);
\item AC voltage (outlet standard);
\item Power demand from the house;
\item Surge demand from the house;
\item Energy consumption from the house.
\end{itemize}

@@

ESBMC can be downloaded from its GitHub in \url{https://github.com/esbmc/esbmc}. Installation commands can be found in \url{https://ssvlab.github.io/esbmc/documentation.html}. There is just the Linux version of the verifier.

\bigskip
\fbox{\parbox{\textwidth}{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3.}}
\bigskip

@@

\bigskip
\fbox{\parbox{\textwidth}{The command-line in Linux is: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c.}} 
\bigskip
